---
title: "Web Exercises"
output: webex::webex_default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!requireNamespace("webex")) {
  stop("You must have the 'webex' package installed to knit HTML from this template.\n   devtools::install_github(\"psyteachr/webex\")")
} else {
  library("webex")
}
```

This is a Web Exercise template created by the [psychology teaching team at the University of Glasgow](http://www.psy.gla.ac.uk), based on ideas from [Software Carpentry](https://software-carpentry.org/lessons/). This template shows how instructors can easily create interactive web documents that students can use in self-guided learning.

The webex package provides a number of functions that you use in [inline R code](https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf) to create HTML widgets (text boxes, pull down menus, buttons that reveal hidden content). Examples are given below. Knit this file to HTML to see how it works.

**NOTE: To use the widgets in the compiled HTML file, you need to have a JavaScript-enabled browser. The widgets don't work in the built-in RStudio browser. In the built-in browser, click the "Open in Browser" button to open the file in your operating system's browser.**

## Fill-In-The-Blanks (`fitb()`)

Create fill-in-the-blank questions using `fitb()`, providing the answer as the first argument.

- 2 + 2 is `r fitb("4")`

You can also create these questions dynamically, using variables from your R session.

```{r echo = FALSE}
x <- sample(2:8, 1)
```

- The square root of `r x^2` is: `r fitb(x)`

The blanks are case-sensitive; if you don't care about case, use the argument `ignore_case = TRUE`.

- What is the letter after D? `r fitb("E", ignore_case = TRUE)`

If you want to ignore differences in whitespace use, use the argument `ignore_ws = TRUE` (which is the default) and include spaces in your answer anywhere they could be acceptable.

- How do you load the tidyverse package? `r fitb(c("library( tidyverse )", "library( \"tidyverse\" )", "library( 'tidyverse' )"), ignore_case = TRUE, width = "20", regex = TRUE)`

You can set more than one possible correct answer by setting the answers as a vector.

- Type a vowel: `r fitb(c("A", "E", "I", "O" , "U"), ignore_case = TRUE)`

## Multiple Choice (`mcq()`)

- "Never gonna give you up, never gonna: `r mcq(c("let you go", "turn you down", "run away", answer = "let you down"))`"
- "I `r mcq(c(answer = "bless the rains", "guess it rains", "sense the rain"))` down in Africa" -Toto

## True or False (`torf()`)

- True or False? You can permute values in a vector using `sample()`. `r torf(TRUE)`

## Hidden solutions and hints

You can fence off a solution area that will be hidden behind a button using `hide()` before the solution and `unhide()` after, each as inline R code.  Pass the text you want to appear on the button to the `hide()` function.

If the solution is an RMarkdown code chunk, instead of using `hide()` and `unhide()`, simply set the `webex.hide` chunk option to TRUE, or set it to the string you wish to display on the button.

### Example problem

**Recreate the scatterplot below, using the built-in `cars` dataset.**

```{r echo = FALSE}
with(cars, plot(speed, dist))
```

`r hide("I need a hint")`
See the documentation for `plot()` (`?plot`)
`r unhide()`

<!-- note: you could also just set webex.hide to TRUE -->

```{r eval = FALSE, webex.hide="Click here to see the solution"}
plot(cars$speed, cars$dist)
```

<!-- TO CHANGE WIDGET COLOURS:
  move command below out of this HTML comment area
  and then re-compile;
  unfilled becomes yellow, correct becomes pink 
     
`r style_widgets("#FFFF00", "#FF3399")`
-->

<br><br><br>

## Und jetzt in Java-Script

<h1>Teste dich!</h1>
<main id="main">
	<form id="quiz" action="">
		<p id="intro">Wie gut kannst du Wahrscheinlichkeiten einschätzen?</p>
	</form>
</main>
	

```{css, echo=FALSE}
h1 {
	background: #f1f3f4 none repeat scroll 0 0 !important;
	padding: 1rem !important;
}

#quiz ul {
	list-style: none;
	margin: 0;
	padding: 0;
}

#quiz li {
	margin: 0;
	padding: 0;
}

#quiz label {
	display: block;
	background-color: #cae1ff;
	border: 2px solid black;
	border-radius: 0.2em;
	margin: 0.1em 0;
	padding: 1em 2em;
	text-align: start;
	max-width: 25em;
}

#quiz label:hover {
	background-color: #a4d3ee;
}

#quiz input:checked ~ label,
#quiz input:focus ~ label {
	background-color: #87cefa;
	border-color: solid black;
}

#quiz input {
	left: -9999px;
	position: absolute;
}

#quiz button:not(.startBtn) {
	display: none;
}

#quiz button,
#quiz label {
	cursor: pointer;
}
/* listing with solutions */

.question {
	font-weight: bold;
}

.correct {
	color: #0c0;
}

.wrong {
	color: #c00;
}

.correct:before {
	content: '✓';
	color: #0d0;
}

.wrong:before {
	content: '✗';
	color: #f00;
}

.correct:before,
.wrong:before {
	font: 2em bold;
	padding: 0 0.2em;
}

#scores,
#scores td,
#scores th {
	border: 1px solid black;
	border-collapse: collapse;
	text-align: center;
}

```


```{js, echo=FALSE}
// https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global_Objects/Array/from#Polyfill
// Production steps of ECMA-262, Edition 6, 22.1.2.1
if (!Array.from) {
	Array.from = (function () {
		var toStr = Object.prototype.toString;
		var isCallable = function (fn) {
			return typeof fn === 'function' || toStr.call(fn) === '[object Function]';
		};
		var toInteger = function (value) {
			var number = Number(value);
			if (isNaN(number)) {
				return 0;
			}
			if (number === 0 || !isFinite(number)) {
				return number;
			}
			return (number > 0 ? 1 : -1) * Math.floor(Math.abs(number));
		};
		var maxSafeInteger = Math.pow(2, 53) - 1;
		var toLength = function (value) {
			var len = toInteger(value);
			return Math.min(Math.max(len, 0), maxSafeInteger);
		};
		// The length property of the from method is 1.
		return function from(arrayLike /*, mapFn, thisArg */ ) {
			// 1. Let C be the this value.
			var C = this;
			// 2. Let items be ToObject(arrayLike).
			var items = Object(arrayLike);
			// 3. ReturnIfAbrupt(items).
			if (arrayLike === null) {
				throw new TypeError(
					"Array.from requires an array-like object - not null or undefined");
			}
			// 4. If mapfn is undefined, then let mapping be false.
			var mapFn = arguments.length > 1 ? arguments[1] : void undefined;
			var T;
			if (typeof mapFn !== 'undefined') {
				// 5. else
				// 5. a If IsCallable(mapfn) is false, throw a TypeError exception.
				if (!isCallable(mapFn)) {
					throw new TypeError(
						'Array.from: when provided, the second argument must be a function');
				}
				// 5. b. If thisArg was supplied, let T be thisArg; else let T be undefined.
				if (arguments.length > 2) {
					T = arguments[2];
				}
			}
			// 10. Let lenValue be Get(items, "length").
			// 11. Let len be ToLength(lenValue).
			var len = toLength(items.length);
			// 13. If IsConstructor(C) is true, then
			// 13. a. Let A be the result of calling the [[Construct]] internal method 
			// of C with an argument list containing the single item len.
			// 14. a. Else, Let A be ArrayCreate(len).
			var A = isCallable(C) ? Object(new C(len)) : new Array(len);
			// 16. Let k be 0.
			var k = 0;
			// 17. Repeat, while k < len… (also steps a - h)
			var kValue;
			while (k < len) {
				kValue = items[k];
				if (mapFn) {
					A[k] = typeof T === 'undefined' ? mapFn(kValue, k) : mapFn.call(T,
						kValue, k);
				} else {
					A[k] = kValue;
				}
				k += 1;
			}
			// 18. Let putStatus be Put(A, "length", len, true).
			A.length = len;
			// 20. Return A.
			return A;
		};
	}());
}
'use strict';
var myQuiz = {
	container: null,
	// helper function
	createElement: function (o) {
		var el, p;
		if (o && (o.tag || o.tagName)) {
			el = document.createElement(o.tag || o.tagName);
			if (o.text || o.txt) {
				var text = (o.text || o.txt)
				el.innerHTML = text;
			}
			for (p in o) {
				if (!p.match(/^t(e)?xt|tag(name)?$/i)) {
					el[p] = o[p];
				}
			}
		}
		return el;
	},
	// user interface for a quiz question
	createOptions: function () {
		var t = this,
			options = [],
			ul = document.createElement("ul");
		t.emptyContainer();
		t.intoContainer(t.createElement({
			tag: "h2",
			text: t.currentQuestion.question
			<!-- text: "(" + t.currentQuestion.category + ") " + t.currentQuestion.question -->
		}));
		t.intoContainer(ul);
		// create options
		options.push(t.currentQuestion.solution);
		t.currentQuestion.falses.forEach(function (s) {
			options.push(s);
		});
		t.shuffleArray(options);
		options.forEach(function (s, i) {
			var li = document.createElement("li"),
				label = t.createElement({
					htmlFor: "a" + t.questions.length + "_" + i,
					tag: "label",
					text: s
				}),
				radio = t.createElement({
					id: "a" + t.questions.length + "_" + i,
					name: "answer",
					tag: "input",
					type: "radio",
					tabindex: "0",
					value: s
				});
			ul.appendChild(li);
			li.appendChild(radio);
			li.appendChild(label);
		});
		// Hinweis für Tastatur-User
		t.intoContainer(t.createElement({
			tag: "button",
			text: "confirm choice",
			type: "submit"
		}));
	},
	currentChoices: [],
	currentQuestion: null,
	// data could be filled from an external source (JSON)
	data: [{
		<!-- category: '1', -->
		question: 'Wie berechnet man den Flächeninhalt eines Dreiecks?',
		solution: 'A= bla blubb blabla',
		falses: ['A=b+c',
			'darf man hier auch was anders',
			'tja kein tex'],
		explanation: 'Erklärung hier'
	}, {
		<!-- category: '2', -->
		question: 'Was ist wahrscheinlicher',
		solution: 'dass er das macht',
		falses: ['2', '3', '4'],
		explanation: 'Erklärung hier'
	}, {
		<!-- category: '4', -->
		question: 'Was soll ich noch fragen',
		solution: 'viel',
		falses: ['heute nichts mehr',
			'dies oder das',
			'egal, alles gleich gut'],
	}],
	emptyContainer: function () {
		var t = this;
		while (t.container.firstChild) {
			t.container.removeChild(t.container.firstChild);
		}
	},
	handleInput: function () {
		var t = this, // t points to myQuiz
			// create real array so we can use forEach
			inputs = Array.from(t.container.getElementsByTagName("input")),
			selectedSolution = "";
		// determine selection
		inputs.forEach(function (o) {
			if (o.checked) {
				selectedSolution = o.value;
			}
		});
		// process selected answer
		if (selectedSolution && t.currentQuestion) {
			t.currentChoices.push({
				a: selectedSolution,
				q: t.currentQuestion
			});
			t.play();
		}
		// accept start button
		if (!t.currentQuestion) {
			t.play();
		}
	},
	init: function () {
		var t = this;
		// here goes any code for loading data from an external source
		t.container = document.getElementById("quiz");
		if (t.data.length && t.container) {
			// use anonymous functions so in handleInput
			// "this" can point to myQuiz
			t.container.addEventListener("submit", function (ev) {
				t.handleInput();
				ev.stopPropagation();
				ev.preventDefault();
				return false;
			});
			t.container.addEventListener("mouseup", function (ev) {
				// we want to only support clicks on start buttons...
				var go = ev.target.tagName.match(/^button$/i);
				// ... and labels for radio buttons when in a game
				if (ev.target.tagName.match(/^label$/i) && t.currentQuestion) {
					go = true;
				}
				if (go) {
					window.setTimeout(function () {
						t.handleInput();
					}, 50);
					ev.stopPropagation();
					ev.preventDefault();
					return false;
				}
			});
			t.start();
		}
	},
	intoContainer: function (el, parentType) {
		var t = this,
			parent;
		if (!el) {
			return;
		}
		if (parentType) {
			parent = document.createElement(parentType);
			parent.appendChild(el);
		} else {
			parent = el;
		}
		t.container.appendChild(parent);
		return parent;
	},
	// ask next question or end quiz if none are left
	play: function () {
		var t = this,
			ol;
		// game over?
		if (!t.questions.length) {
			t.showResults();
			// offer restart
			window.setTimeout(function () {
				t.start();
			}, 50);
			return;
		}
		t.currentQuestion = t.questions.shift();
		t.createOptions();
	},
	// list with remaining quiz question objects
	questions: [],
	// list original questions and given answers and elaborate on solutions
	showResults: function () {
		var cat, ol, s, scores = {},
			t = this,
			tab, thead, tbody, tr;
		t.emptyContainer();
		// show message
		t.intoContainer(t.createElement({
			tag: "p",
			text: "Du hast alle Quizfragen beantwortet. Hier kommt die Auswertung:"
		}));
		// list questions and given answers
		ol = t.intoContainer(t.createElement({
			id: "result",
			tag: "ol"
		}));
		t.currentChoices.forEach(function (o) {
			var p, li = ol.appendChild(t.createElement({
				tag: "li"
			}));
			// list original question
			li.appendChild(t.createElement({
				className: "question",
				tag: "p",
				text: o.q.question
				<!-- text: "(" + o.q.category + ") " + o.q.question -->
			}));
			// list given answer
			p = li.appendChild(t.createElement({
				tag: "p",
				text: "Deine Antwort: "
			}));
			p.appendChild(t.createElement({
				className: (o.q.solution == o.a ? "correct" : "wrong"),
				tag: "em",
				text: o.a
			}));
			// wrong answer?
			if (o.q.solution != o.a) {
				p = li.appendChild(t.createElement({
					tag: "p",
					text: "Die richtige Antwort wäre gewesen: "
				}));
				p.appendChild(t.createElement({
					tag: "em",
					text: o.q.solution
				}));
			}
			// elaborate on solution?
			if (o.q.explanation) {
				p = li.appendChild(t.createElement({
					tag: "p",
					text: "Erläuterung: "
				}));
				p.appendChild(t.createElement({
					tag: "em",
					text: o.q.explanation
				}));
			}
		});
		// display a kind of percentual score over the categories
		cat = [];
		t.currentChoices.forEach(function (o) {
			if (!cat.includes(o.q.category)) {
				cat.push(o.q.category);
			}
		});
		cat.sort();
		cat.forEach(function (c) {
			var correct = 0,
				num = 0;
			t.currentChoices.forEach(function (o) {
				if (o.q.category == c) {
					num++;
					if (o.q.solution == o.a) {
						correct++;
					}
				}
			});
			scores[c] = Math.floor(100 * correct / num) + "%";
		});
		tab = t.intoContainer(t.createElement({
			id: "scores",
			tag: "table"
		}));
		<!-- tab.appendChild(t.createElement({ -->
		<!-- 	tag: "caption", -->
		<!-- 	text: "Übersicht nach Kategorien" -->
		<!-- })) -->
		<!-- thead = tab.appendChild(t.createElement({ -->
		<!-- 	tag: "thead" -->
		<!-- })) -->
		<!-- tr = thead.appendChild(t.createElement({ -->
		<!-- 	tag: "tr" -->
		<!-- })) -->
		<!-- for (s in scores) { -->
		<!-- 	tr.appendChild(t.createElement({ -->
		<!-- 		tag: "th", -->
		<!-- 		text: s -->
		<!-- 	})); -->
		<!-- } -->
		<!-- tbody = tab.appendChild(t.createElement({ -->
		<!-- 	tag: "tbody" -->
		<!-- })) -->
		<!-- tr = tbody.appendChild(t.createElement({ -->
		<!-- 	tag: "tr" -->
		<!-- })) -->
		<!-- for (s in scores) { -->
		<!-- 	tr.appendChild(t.createElement({ -->
		<!-- 		tag: "td", -->
		<!-- 		text: scores[s] -->
		<!-- 	})); -->
		<!-- } -->
		// show message
		t.intoContainer(t.createElement({
			tag: "p",
			text: "Nochmal?"
		}));
	},
	// helper function: shuffle array (adapted from http://javascript.jstruebig.de/javascript/69)
	shuffleArray: function (a) {
		var i = a.length;
		while (i >= 2) {
			var zi = Math.floor(Math.random() * i);
			var t = a[zi];
			a[zi] = a[--i];
			a[i] = t;
		}
		// no return argument since the array has been
		// handed over as a reference and not a copy!
	},
	// start quiz with a start button
	start: function () {
		var t = this;
		// fill list of remaining quiz questions
		t.questions = [];
		t.data.forEach(function (o) {
			t.questions.push(o);
		});
		t.shuffleArray(t.questions);
		t.currentChoices = [];
		t.currentQuestion = null;
		// install start button
		t.intoContainer(t.createElement({
			className: "startBtn",
			tag: "button",
			text: "Los geht's!"
		}), "p");
	}
};
document.addEventListener("DOMContentLoaded", function () {
	myQuiz.init();
});


```

<br><br><br>

## Noch mehr Java-Script

Zeigt nur eine Millisek. an. - Funktioniert also nicht

<!-- <h1>JavaScript is ______ Language.</h1><br> -->
<!-- <form > -->
<!-- <input type="radio" name="choice" value="Scripting" required> Scripting -->
<!-- <input type="radio" name="choice" value="Programming"> Programming -->
<!-- <input type="radio" name="choice" value="Application"> Application -->
<!-- <input type="radio" name="choice" value="None of These"> None of These -->
<!-- <input type="submit" value="submit" onclick="validate()"> -->
<!-- </form> -->

<!-- ```{js, echo=FALSE} -->
<!-- document.getElementById("answer").innerHTML; -->
<!-- var submitAnswer = function() { -->

<!--   var radios = document.getElementsByName('choice'); -->
<!--   var val= ""; -->
<!--   for (var i = 0, length = radios.length; i < length; i++) { -->
<!--       if (radios[i].checked) { -->
<!--          val = radios[i].value;  -->
<!--          break; -->
<!--        } -->
<!--   } -->

<!--   if (val == "" ) { -->
<!--     document.getElementById("answer").innerHTML = "please select choice answer"; -->
<!--   } else if ( val == "Scripting" ) { -->
<!--     document.getElementById("answer").innerHTML = "Answer is correct !" -->
<!--   } else { -->
<!--     document.getElementById("answer").innerHTML = "Answer is wrong" -->
<!--   } -->
<!-- }; -->


<!-- ``` -->


